My title

### 2023-03-24 outputs/paper/paper.qmd
draft of regression model, some edits to qmd
kinda started the data section for the valence testing

Antonoff is prolific, to the extent that it is starting to bother people. He has produced and co-produced music for Lorde, Taylor Swift, Florence and the Machine, The Chicks, Clairo, The 1975, Grimes, Zayn, Pink, Lana Del Rey, Olivia Rodrigo, Minions: The Rise of Gru Soundtrack, and more. All of this and his own bands too: Bleachers, and Fun.

@@

However, it's hard to gauge exactly what variables like "danceability" or "valence" mean, even using the documentation. For instance, "valence" is described as "A measure from 0.0 to 1.0 describing the musical positiveness conveyed by a track. Tracks with high valence sound more positive (e.g. happy, cheerful, euphoric), while tracks with low valence sound more negative (e.g. sad, depressed, angry)", and danceability as "how suitable a track is for dancing based on a combination of musical elements including tempo, rhythm stability, beat strength, and overall regularity. A value of 0.0 is least danceable and 1.0 is most danceable". Neither of these definitions fully cover what metrics and thresholds go into something like "danceability". However, whatever these features capture is easier to compare across artists in visualizations than more granular details about bars, beats, duration, and tatums -- a word I just learned, which refers to "the lowest regular pulse train that a listener intuitively infers from the timing of perceived musical events". The full documentation for each variable included in this study is available in the Appendix.

>>>>

Antonoff is prolific, to the extent that it is starting to bother people. He has produced and co-produced music for Lorde, Taylor Swift, Florence and the Machine, The Chicks, Clairo, The 1975, Grimes, Zayn, Pink, Lana Del Rey, Olivia Rodrigo, Minions: The Rise of Gru Soundtrack, and more. All of this and his own bands too: Bleachers, and fun.

@@

However, it's hard to gauge exactly what variables like "danceability" or "valence" mean, even using the documentation. For instance, "valence" is described as "A measure from 0.0 to 1.0 describing the musical positiveness conveyed by a track. Tracks with high valence sound more positive (e.g. happy, cheerful, euphoric), while tracks with low valence sound more negative (e.g. sad, depressed, angry)".

This is pretty vague. I compared the valence scores of classical music tracks to see if this score is based on lyrics, or the audio itself.

and danceability as "how suitable a track is for dancing based on a combination of musical elements including tempo, rhythm stability, beat strength, and overall regularity. A value of 0.0 is least danceable and 1.0 is most danceable". Neither of these definitions fully cover what metrics and thresholds go into something like "danceability". However, whatever these features capture is easier to compare across artists in visualizations than more granular details about bars, beats, duration, and tatums -- a word I just learned, which refers to "the lowest regular pulse train that a listener intuitively infers from the timing of perceived musical events". The full documentation for each variable included in this study is available in the Appendix.
